\hyphenpenalty=10000
\documentclass[margin,10pt]{res} % default is 10 pt
% margin option puts section titles to left of text
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
% \usepackage{txfonts}
\usepackage{ragged2e}

\begin{document}
\name{Jacob Swartz - Full Stack Developer\\[12pt]} % the \\[12pt] adds a blank line after name

\address{515 Central Avenue \#T \\ Mountain View, CA 94043\\ (415) 766-1867}
\address{jacob@swartz.id \\ www.linkedin.com/in/jacobswartz \\
	www.github.com/jjaaccoobb }

\begin{resume}

	\section{OBJECTIVE}
	Eager and experienced full stack developer with a frontend focus. Specialized experience with ecommerce solutions and SEO \& SEM. Intuition for detail and visual aesthetics. Highly self-motivated - strong individual contributor and key asset to any team, with a passion, share knowledge, learn from others, and improve \& expand skill sets.

	\section{EXPERIENCE}
	 {\bf EdCast, Mountain View, CA} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Senior Software Engineer}     &      Nov. 2018-Present
	\end{ncolumn}

	\begin{itemize}
		\item Developed responsive front-end experiences using Node, ES6, React, Redux, D3.js, SCSS
		\item Agile environment with bi-weekly production deployments to over two million monthly active users
		\item Present feature demos directly with customers, assist requirements gathering \& analysis
		\item Maintained code ownership of numerous repositories with hundreds of contributors
		\item Replaced Drupal CMS with static solution using React, supporting seven languages hosted on AWS EC2

	\end{itemize}
	{\bf Walmart Labs, Sunnyvale, CA} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Senior Frontend Software Engineer}     &      Dec. 2017-Jul. 2018
	\end{ncolumn}

	\begin{itemize}
		\item Played key role implementing Walmart.com  multi-tentant site redesign (Mobile + Web), on an agile team owning all Customer Accounts components
		\item Implemented code coverage analysis using Istanbul, automation \& unit testing with Karma/Mocha/Enzyme, Nightwatch.js, orchestrated Magellan
		\item Defined strict and sensible acceptance criteria for pull requests/code reviews
		\item Collaborated with design team \& product designers to author UI/UX style guides
	\end{itemize}

	{\bf The Internet} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Freelance Consultant} &   Jan. 2015-Present
	\end{ncolumn}

	\begin{itemize}
		\item Build websites using Node.js, PHP7, HTML5, CSS3, ES6 JavaScript
		\item Set up Apache/nginx servers for front- and back-end services
		\item Generate ad-hoc reports using MySQL data from ecommerce solutions
		\item Create and manage email campaigns using MailChip/Campaign Monitor
	\end{itemize}

	{\bf Bluestone Creative, Cincinnati, OH} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Creative Technologist} &   Aug. 2014-Sep. 2014
	\end{ncolumn}

	\begin{itemize}
		\item Created websites using HTML5, PHP, JavaScript, Sass \& Foundation
		\item Managed in-house web, DB, storage, and FTP servers
		\item Spearheaded and trained team on tools for project management and bug tracking
	\end{itemize}

	\begin{FlushRight}
		\textit{Continued on next page...}\pagebreak
	\end{FlushRight}

	{\bf Ask.com (InterActive Corp), Oakland, CA} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Software Engineer} &   Oct. 2012-Jul. 2013
	\end{ncolumn}

	\begin{itemize}
		\item Front- and back-end on an agile team owning over twenty domain-specific search results pages (SERPs)
		\item Repaired revenue-generating sites penalized by Google's ranking algorithm "Panda"
		\item Made Questions \& Answers product mobile friendly using responsive design practices
		\item Assisted designers and creative directors in authoring unified style guides
	\end{itemize}

	{\bf FontShop International, San Francisco, CA} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Web Developer} &   Oct. 2008-Jul. 2012
	\end{ncolumn}

	\begin{itemize}
		\item Helped organize \& run TYPO San Francisco | one of Europe's most successful design conferences | for its U.S. premiere at Yerba Buena Center for the Arts
		\item Created responsive e-commerce experiences with PHP5, HTML5, CSS3, JavaScript
		\item Developed font rendering tool for sampling over 100,000 typefaces using php-gd
		\item Implemented internationalization \& localization supporting four languages
		\item Created a shopping cart \& checkout system using CyberSource, Ogone, and PayPal
		\item Migrated from Flash typography hacks by early-adopting webfonts via TypeKit
		\item Maintained self-hosted WordPress blog extended with custom features
	\end{itemize}

	{\bf Fish Flirt Marketing} \\
	\begin{ncolumn}{2} % produces two equally spaced columns
		\underline{Web Developer} &   May 2007-Oct. 2008
	\end{ncolumn}


	\begin{itemize}
		\item Developed ecommerce sites using the LAMP stack, W3C-compliant HTML, CSS, and JavaScript
		\item Installed, configured, and managed SVN/web/mail servers
	\end{itemize}


	\section{EDUCATION}       Sinclair Community College  \\
	Dayton, Ohio; Apr. 2007 | Oct. 2008 \\
	AAS, Computer Information Systems

\end{resume}
\end{document}\textbf{}